EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-01 draft.tex
Justifying containers vs vms, closes #13

The main advantage of container deployments over virtual machine
instances is that they add much less overhead to communication between
them, and they are much more economical to deploy. Scaling and
monitoring can be done much more easily through cloud orchestration
systems such as Kubernetes; these are the reasons why we chose it for
this work.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario
% Did you finally? - JJ
% I did not, will add and assign it - M 
In this section, we propose a design of a reactive container-based application
for executing multi-population based optimization experiments.  For the design,
we followed the design patterns highlighted in the previous section, and again
we can go back to Figure \ref{fig:kafkEO} and use it as a guide for explaining
the main components and their interactions.

>>>>

% The main advantage of container deployments over virtual machine
% instances is that they add much less overhead to communication between
% them, and they are much more economical to deploy. Scaling and
% monitoring can be done much more easily through cloud orchestration
% systems such as Kubernetes; these are the reasons why we chose it for
% this work.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario
% Did you finally? - JJrehe
% I did not, will add and assign it - M
There are many advantages of container-based architectures over one
based on virtual machines. The main ones are architectural: it makes
the design of an application gravitate towards a set of decoupled
tasks, that use reactive, event based programming, to interact with
the rest of the application; containers hold micro-services that are
much easier to test, integrate and deploy. It also simplifies
the interaction APIs. Of course, that makes them more economical in a
pay-per-use cloud provider, but that is not the main reason why we
have chosen them in this paper; reproductibility of experiments and a
clear and idempotent description of the architecture through docker
compose are the main reasons.

In this section, we propose a design of a reactive container-based application
for executing multi-population based optimization experiments.  For the design,
we followed the design patterns highlighted in the previous section, and again
we can go back to Figure \ref{fig:kafkEO} and use it as a guide for explaining
the main components and their interactions.
